Presentation Title

### 2017-04-24 chapters/ch2-checkpoint.tex
Privacy preserving validation

>>>>

\section{Privacy}
Currently the validation protocol requires TX blocks to be sent in full. We can
do better by modifying how the chain is computed to enhance user's privacy.
First, recall that hash pointers are calculated on the whole block (TX or CP),
i.e. $\texttt{h}(b_{s, h_s})$. In the validation stage, $b_{s, h_s}$ must be
provided to recompuate the digest and check that it matches the block at $h_s - 1$.
To improve this algorithm, we introduce a new property \emph{digest} for each
block, which simply is $d_{s, h_s} = \texttt{h}(b_{s, h_s})$, $d$ is computed
dynamically. Then the chain of hash pointers is formed using $\texttt{h}(d_{s,
  h_s})$. During the validation phase, there is no need to provide the complete
block, only the \emph{digest} is sufficient. Of course, the pair of the TX of
interest must be provided in full.
